---
title: "Install, explore and test package for review"
author: 
  - Matt Mulvahill
  - Colorado Biostatistical Consortium - Department of Biostatistics - CSPH
date: "9/25/2017"
output: 
  bookdown::html_document2:
    theme: simplex
    toc: true
    toc_float: 
      collapsed: false
    number_sections: true
  md_document:
    variant: markdown_github
---


```{r}
library(devtools)
library(knitr)
knitr::opts_chunk$set(echo    = TRUE,
                      message = TRUE,
                      warning = TRUE,
                      results = 'markup',
                      cache   = TRUE)
```

# Overall comments

(Not sure if I should include this)
- Do you plan on submitting to Bioconductor?  If so, use installation process in README.md:

```{r install-rec, eval=FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite()
# devtools::install_github("MahShaaban/cRegulome")
```

- Just included database and connect to it? Instead of `get_db() from a personal dropbox account?`
- Something strange is happening with `print.tbl_df` on `dat_tf` in vignetted.
  Works after `class(dat_tf)` is run, but not before.

# Devtools checking

- Added cRegulome as submodule -- installing from there.



## `install()`

Install as-is in latest commit.

```{r asisinstall}
devtools::install("./lib/cRegulome", build_vignettes = TRUE)
```

Commit 5d6e698 installs without error.



## `document()`

Run devtools/roxygen2 document function to see if it makes any changes to
roxygen2 generated files (NAMESPACE, man/, etc.). 

```{r devtools-document}
devtools::document("./lib/cRegulome")
```

Note, package imports `dbplyr`, `R.utils`, and `RSQLite` were deleted from
NAMESPACE.

- [ ] Looks like the package `dbplyr` is only used in the vignette and manuscript
  -- consider moving to Suggests from Imports.
- [ ] The `R.utils::gunzip` function is used in many places (vignette, manuscript,
  unrun example), but is not actually used in the package code. Consider moving
  to suggests or adding a roxygen2 line to import the function (in the
  `get_tf()` documentation: `#' @importFrom R.utils gunzip`.
- [ ] `RSQLite::SQLite()` has the same situation as `gunzip` above, except that it
  is used in examples executed with `devtools::check()`.  Consider adding an 
  `#' @importFrom RSQLite SQLite` line to documentation of functions that use
  this function in examples.

Either of the `@importFrom` suggestions could be `@import <pkgname>` also,
though the former is preferable to avoid name conflicts.

## `check()`

```{r devtools-check}
devtools::check("./lib/cRegulome")
```

Notes -- 
- [ ] Add .git/ to the .Rbuildignore
- [ ] "Package unavailable to check Rd xrefs: 'targetscan.Hs.eg.db' -- resolves if
  targetscan.hs.eg.db is installed from bioconductor (doesn't have to be
  loaded). Doesn't affect installation. 

## Spell check

```{r devtools-check, echo=TRUE}
devtools::spell_check("./lib/cRegulome")
```

A few mispelled words throughout.  Run `spell_check()` and resolve.

# Other checks

## `goodpractice::gp()`

```{r goodpractice, eval=FALSE}
if (!require(goodpractice)) devtools::install_github("MangoTheCat/goodpractice", ref = "v1.0.1")
library(goodpractice)
gp("./lib/cRegulome")
```

Nothing new here.  Results: 1. More unit tests 2. Imports in NAMESPACE 3. .git
directory.






# Session Info
```{r sessioninfo, echo=TRUE}
sessionInfo()
```
